---
title: "integrated_liver"
author: "Núria Rivera Brugués"
date: "2023-11-26"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache=F)
```

```{r}
library(Seurat)
library(sp)
library(Matrix)
library(SeuratObject)
library(patchwork)
library(dplyr)
library(tidyverse)
library(ggplot2) # plots
library(magrittr) # %>% operator
library(reticulate) # required for "leiden" clustering
library(enrichR) # functional enrichment
library(future) # multicore support for Seurat
library(cowplot)
library(SingleCellExperiment)
library(clusterProfiler)
library(org.Hs.eg.db)

```

```{r}
dir1<-"/home/nrb/Escritorio/perAnna/18_hepato/14414522_C41_TST_raw_data/"
dir2<-"/home/nrb/Escritorio/perAnna/18_hepato/14414525_C41_SC_raw_data/"
matrix_obj_C41_TST<-Read10X(dir1, unique.features = TRUE, strip.suffix = TRUE)
matrix_obj_C41_TST[1:10, 1:19]
matrix_obj_C41_SC<-Read10X(dir2, unique.features = TRUE, strip.suffix = TRUE)
matrix_obj_C41_SC[1:10, 1:19]
seurat_C41_TST = CreateSeuratObject(counts =  matrix_obj_C41_TST, project = "TST", min.cells = 5, min.features = 200)
seurat_C41_SC = CreateSeuratObject(counts =  matrix_obj_C41_SC, project = "SC", min.cells = 5, min.features = 200)

sc.sn1 <- merge(seurat_C41_SC, y = seurat_C41_TST, add.cell.ids = c("SC", "TST"), project = "sc.sn1")
sc.sn1
head(colnames(sc.sn1))
table(sc.sn1$orig.ident)

# Get cell names
TST.cell_names <- grep(pattern = "^TST", x = colnames(sc.sn1), value = T)
SC.cell_names <- grep(pattern = "^SC", x = colnames(sc.sn1), value = T)

# Create new meta.data column
sc.sn1@meta.data$Fraction[colnames(sc.sn1) %in% TST.cell_names] <- "TST"
sc.sn1@meta.data$Fraction[colnames(sc.sn1) %in% SC.cell_names] <- "SC"
saveRDS(sc.sn1, file = "sc.sn41.rds")
```



```{r}
sc.sn41 <- readRDS("sc.sn41.rds")
head(colnames(sc.sn41))
table(sc.sn41$orig.ident)
```

## QC and selecting cells for further analysis
```{r}
pbmc<-sc.sn41
pbmc[["percent.mt"]] <- PercentageFeatureSet(pbmc, pattern = "^MT-")
```


```{r}
# Visualize QC metrics as a violin plot
pdf(paste("QC",sep=""))
VlnPlot(pbmc, features = c("nFeature_RNA", "nCount_RNA","percent.mt"), ncol = 3)
dev.off()
VlnPlot(pbmc, features = c("nFeature_RNA", "nCount_RNA","percent.mt"), ncol = 3)
```


```{r}
# FeatureScatter is typically used to visualize feature-feature relationships, but can be used
# for anything calculated by the object, i.e. columns in object metadata, PC scores etc.

plot1 <- FeatureScatter(pbmc, feature1 = "nCount_RNA", feature2 = "percent.mt")
plot2 <- FeatureScatter(pbmc, feature1 = "nCount_RNA", feature2 = "nFeature_RNA")
pdf(paste("scatter_features",sep=""))
plot1 + plot2
dev.off()

plot1 + plot2
```

```{r}
pbmc <- subset(pbmc, subset = nFeature_RNA > 200 & nFeature_RNA < 8000 & percent.mt < 80 )
```

# Normalizing the data

```{r}
pbmc <- NormalizeData(pbmc, normalization.method = "LogNormalize", scale.factor = 10000)
```


# Identification of highly variable features (feature selection)
```{r}
pbmc <- FindVariableFeatures(pbmc, selection.method = "vst", nfeatures = 2000)

# Identify the 10 most highly variable genes
top10 <- head(VariableFeatures(pbmc), 10)

# plot variable features with and without labels
plot1 <- VariableFeaturePlot(pbmc)+ NoLegend()
plot2 <- LabelPoints(plot = plot1, points = top10, repel = TRUE)+ NoLegend()
pdf(paste("variable.features",sep=""))
plot_grid(plot1 + plot2)
dev.off()

plot_grid(plot1 + plot2)
```





```{r}
sc.sn1.list <- SplitObject(sc.sn41, split.by = "Fraction")
features <- SelectIntegrationFeatures(object.list = sc.sn1.list)
sc.sn1.list <- lapply(X = sc.sn1.list, FUN = function(x) {
  x <- NormalizeData(x, normalization.method = "LogNormalize", scale.factor = 10000)
  x <- ScaleData(x, features = features, verbose = FALSE)
  x <- RunPCA(x, features = features, verbose = FALSE)
})

liver.anchors <- FindIntegrationAnchors(object.list = sc.sn1.list, dims = 1:30)

liver.integrated <- IntegrateData(anchorset = liver.anchors, dims = 1:30)

```

```{r}
library(ggplot2)
library(cowplot)
# switch to integrated assay. The variable features of this assay are automatically
# set during IntegrateData
DefaultAssay(liver.integrated) <- "integrated"

                                        # Run the standard workflow for visualization and clustering
liver.integrated <- ScaleData(liver.integrated, verbose = FALSE)
liver.integrated <- RunPCA(liver.integrated, npcs = 30, verbose = FALSE)
liver.integrated <- RunUMAP(liver.integrated, reduction = "pca", dims = 1:30)
liver.integrated <- RunTSNE(liver.integrated, dims.use = 1:10, do.fast = TRUE)
p1 <- DimPlot(liver.integrated, reduction = "umap", group.by = "Fraction")
p2 <- DimPlot(liver.integrated, reduction = "tsne", group.by = "Fraction") 
pdf(paste("umap.tsne",sep=""))
plot_grid(p1 +p2)
dev.off()
plot_grid(p1 +p2)
```


```{r}
pdf(paste("umap",sep=""))
DimPlot(liver.integrated, reduction = "umap", group.by = "Fraction")
dev.off()
DimPlot(liver.integrated, reduction = "umap", group.by = "Fraction")
```


```{r}
pdf(paste("tsne",sep=""))
DimPlot(liver.integrated, reduction = "tsne", group.by = "Fraction") 
dev.off()
DimPlot(liver.integrated, reduction = "tsne", group.by = "Fraction")
```

```{r}
pdf(paste("Vizdim",sep=""))
VizDimLoadings(liver.integrated, dims = 1:2, reduction = "pca")
dev.off()
VizDimLoadings(liver.integrated, dims = 1:2, reduction = "pca")
```

```{r}
pdf(paste("pca.pdf",sep=""))
DimPlot(liver.integrated, reduction = "pca",group.by = "Fraction")
dev.off()
DimPlot(liver.integrated, reduction = "pca",group.by = "Fraction")
```

```{r}
pdf(paste("heatmap_PCA.pdf",sep=""))
DimHeatmap(liver.integrated, dims = 1, cells = 500, balanced = TRUE)
dev.off()
DimHeatmap(liver.integrated, dims = 1, cells = 500, balanced = TRUE)
```

```{r}
pdf(paste("heatmap_PCA2.pdf",sep=""))
DimHeatmap(liver.integrated, dims = 1:2, cells = 500, balanced = TRUE)
dev.off()
DimHeatmap(liver.integrated, dims = 1:2, cells = 500, balanced = TRUE)
```



```{r}
# Examine and visualize PCA results a few different ways
print(liver.integrated[["pca"]], dims = 1:5, nfeatures = 5)
```


```{r}
# NOTE: This process can take a long time for big datasets, comment out for expediency. More
# approximate techniques such as those implemented in ElbowPlot() can be used to reduce
# computation time
liver.integrated <- JackStraw(liver.integrated, num.replicate = 100)
liver.integrated <- ScoreJackStraw(liver.integrated, dims = 1:20)
```


```{r}
pdf(paste("JackStrawPlot.pdf",sep=""))
JackStrawPlot(liver.integrated, dims = 1:20)
dev.off()
JackStrawPlot(liver.integrated, dims = 1:20)
```



```{r}
pdf(paste("elbowplot.pdf",sep=""))
ElbowPlot(liver.integrated)
dev.off()
ElbowPlot(liver.integrated)
```



# Finding differentially expressed features (cluster biomarkers)


```{r}
# find markers for every cluster compared to all remaining cells, report only the positive ones
liver.integrated.markers <- FindAllMarkers(liver.integrated, only.pos = FALSE, min.pct = 0.25, logfc.threshold = 0.25)
liver.integrated.markers %>% group_by(cluster) %>% top_n(n = 5, wt = avg_log2FC)
write.csv2(liver.integrated.markers, "liver.integrated.markers41.csv")
```

```{r}
clusterSC.markers <- FindMarkers(liver.integrated, ident.1 = "SC", logfc.threshold = 0.25, test.use = "roc", only.pos = FALSE)
head(clusterSC.markers, n = 5)
write.csv2(clusterSC.markers, "clusterSC.markers.csv")
```

```{r}
clusterTST.markers <- FindMarkers(liver.integrated, ident.1 = "TST", logfc.threshold = 0.25, test.use = "roc", only.pos = FALSE)
head(clusterTST.markers, n = 5)
write.csv2(clusterTST.markers, "clusterTST.markers.csv")
```

```{r}
VlnPlot(liver.integrated, features = c("HBA2", "SYDE2"))
```


```{r}
# you can plot raw counts as well
VlnPlot(liver.integrated, features = c("NKG7", "MALAT1"),  log = TRUE)
```


```{r}
FeaturePlot(liver.integrated, features = c("MALAT1", "NKG7", "HBA2", "SYDE2"))
```


```{r}
top10 <- liver.integrated.markers %>% group_by(cluster) %>% top_n(n = 15, wt = avg_log2FC)

pdf(paste("heatmap_clusters.pdf",sep=""))
DoHeatmap(liver.integrated, features = top10$gene) 
dev.off()
DoHeatmap(liver.integrated, features = top10$gene) 
```

```{r}
markers41 <- FindMarkers(liver.integrated, ident.1 = "SC", ident.2 = "TST", verbose = FALSE, assay = "integrated", slot = "scale.data", min.pct = 0.25, test.use = "wilcox", logfc.threshold = 0.25)
head(markers41, n = 5)
```


```{r}
markers41 <- markers41 %>%  arrange(avg_diff)
write.csv2(markers41, "markers41.csv")
```


# ORA


```{r}
matrix_obj_C41_SC<-Read10X(dir2, unique.features = TRUE, strip.suffix = TRUE)
markers41<-read.csv2("./markers41.csv")
markers41 <- markers41 %>%  arrange(avg_diff)
sc.sn41 <- readRDS("sc.sn41.rds")

allEntrezs <- rownames(matrix_obj_C41_SC)
selectedEntrezsUP <- markers41$X
rownames(markers41)<-markers41$X
length(allEntrezs); length(selectedEntrezsUP)


ego <- enrichGO(gene = selectedEntrezsUP, 
                universe = allEntrezs,
                keyType = "SYMBOL",
                OrgDb = org.Hs.eg.db, 
                ont = "BP", 
                pAdjustMethod = "BH", 
                qvalueCutoff = 0.01, 
                readable = TRUE)

```

```{r, warning=FALSE}
head(ego)
ego_results <- data.frame(ego)
write.csv(ego_results, "clusterProfiler_ORAresults_UpGO.csv")
```

```{r, warning=FALSE}
dotplot(ego, showCategory=10)
pdf(paste("dotplot.pdf",sep=""))
dotplot(ego, showCategory=10)
dev.off()
```

```{r, warning=FALSE}
pdf(paste("GO.pdf",sep=""))
goplot(ego, showCategory=5, cex=0.5)
dev.off()

goplot(ego, showCategory=5, cex=0.5)
```

```{r, warning=FALSE}
## Gene network para los términos seleccionados
pdf(paste("cneplot.pdf",sep=""))
cnetplot(ego) 
dev.off()

cnetplot(ego) 
```


```{r, warning=FALSE}

ego2 = clusterProfiler::simplify(ego, cutoff = 0.01, by = "p.adjust")
png("./cnetplot_transp.png", units = "in", width = 24, height = 16, res = 600,
    bg = "transparent")
par(bg = NA)
a <- cnetplot(ego2, showCategory = 5, cex_category = 1, cex_label_category = 2.5,
    cex_gene = 1, cex_label_gene = 1, circular = FALSE, colorEdge = TRUE)
a
invisible(dev.off())
a
```





```{r, warning=FALSE}
## Enrichment Map
library(enrichplot)
ego_sim <- pairwise_termsim(ego)
pdf(paste("emaplot.pdf",sep=""))
emapplot(ego_sim, cex_label_category=0.6)
dev.off()

emapplot(ego_sim, cex_label_category=0.6)
```

```{r, warning=FALSE, fig.width=15, fig.height=15}
term_similarity_matrix = pairwise_termsim(ego)
emapplot(term_similarity_matrix, showCategory = 15, group_category = TRUE, group_legend = TRUE)

pdf(paste("emaplot_grouped.pdf",sep=""),width = 10, height = 10)
emapplot(term_similarity_matrix, showCategory = 15, group_category = TRUE, group_legend = TRUE)
dev.off()
```

```{r, warning=FALSE}
library(enrichplot)
heatplot(ego)

pdf(paste("heatplot_ego.pdf",sep=""),width = 9, height = 10)
heatplot(ego)
dev.off()
```


```{r}
library(geneset)
library(genekitr)

hg_gs <- geneset::getGO(org = "human",ont = "bp")

# ORA analysis
ego3 <- genORA(selectedEntrezsUP, geneset = hg_gs, p_cutoff = 0.01, q_cutoff = 0.01)
# next we only show ten sample terms 
ego3 <- ego3[1:10, ]
head(ego3)
```
# Bar Plot
```{r}
library(patchwork)
p1 <- plotEnrich(ego3, plot_type = "bar")
p2 <- plotEnrich(ego3, plot_type = "bar", term_metric = "GeneRatio", stats_metric = "pvalue")
p3 <- plotEnrich(ego3, plot_type = "bar", up_color = "#E69056", down_color = "#325CAC")
p4 <- plotEnrich(ego3, plot_type = "bar", wrap_length = 25)
p1 + p2 + p3 + p4 + plot_annotation(tag_levels = "A")


pdf(paste("BarPlot.pdf",sep=""))
p1 + p2 + p3 + p4 + plot_annotation(tag_levels = "A")
dev.off()
```

#  Bubble Plot

```{r}
library(patchwork)
p1 <- plotEnrich(ego3, plot_type = "bubble")
p2 <- plotEnrich(ego3, plot_type = "bubble", 
                 scale_ratio = 0.5, stats_metric = "qvalue")
p1 / p2 + plot_annotation(tag_levels = "A")


pdf(paste("BubblePlot.pdf",sep=""))
p1 / p2 + plot_annotation(tag_levels = "A")
dev.off()
```

#  Dot Plot

```{r}
library(patchwork)
p1 <- plotEnrich(ego3, plot_type = "dot")
p2 <- plotEnrich(ego3,
  plot_type = "dot",
  scale_ratio = 0.5,
  stats_metric = "pvalue",
  term_metric = "RichFactor"
)
p1 + p2 + plot_annotation(tag_levels = "A")


pdf(paste("DOTPlot.pdf",sep=""))
p1 + p2 + plot_annotation(tag_levels = "A")
dev.off()
```

```{r}
plotEnrich(ego3,
           plot_type = 'dot',
           scale_ratio = 0.5, # dot size
           main_text_size = 10,
           legend_text_size =8,
           n_term = 6) # show terms


pdf(paste("PlotEnrich.pdf",sep=""))
plotEnrich(ego3,
           plot_type = 'dot',
           scale_ratio = 0.5, # dot size
           main_text_size = 10,
           legend_text_size =8,
           n_term = 6) # show terms
dev.off()
```

#  Lollipop Plot

```{r}
library(patchwork)
p1 <- plotEnrich(ego3, plot_type = "lollipop")
p2 <- plotEnrich(ego3,
  plot_type = "lollipop",
  scale_ratio = .2,
  stats_metric = "pvalue",
  term_metric = "RichFactor",
  up_color = "#a32a31",
  down_color = "#f7dcca"
)
p1 + p2 + plot_annotation(tag_levels = "A")


pdf(paste("Lollipop.pdf",sep=""))
p1 + p2 + plot_annotation(tag_levels = "A")
dev.off()
```


#  Heatmap Plot

```{r}
library(patchwork)
p1 <- plotEnrich(ego3, plot_type = "geneheat")
show_gene = c('MALAT1','ABCC2','ABCC2','ABCC2')
p2 <- plotEnrich(ego3, plot_type = "geneheat", show_gene = show_gene)
p3 <- plotEnrich(ego3, plot_type = "geneheat", show_gene = show_gene)
p1 / p2 / p3 + plot_annotation(tag_levels = "A")

pdf(paste("Heatmapplot.pdf",sep=""))
p1  + plot_annotation(tag_levels = "A")
dev.off()
```

# Wordcloud Plot
```{r}
plotEnrich(ego3, plot_type = "wordcloud")

pdf(paste("Wordcloudplot.pdf",sep=""))
plotEnrich(ego3, plot_type = "wordcloud")
dev.off()
```


# Upset Plot

```{r}
pdf(paste("Upsetplot.pdf",sep=""))
plotEnrich(ego3, plot_type = "upset",main_text_size = 15,legend_text_size = 8)
dev.off()

plotEnrich(ego3, plot_type = "upset",main_text_size = 15,legend_text_size = 8)
```

#  GO-specific: Terms Tangram Plot
```{r}
plotEnrich(ego3, plot_type = "gotangram",main_text_size = 15,legend_text_size = 8, scale_ratio = 0.5, sim_method = "Rel")
#“bar”, “wego”, “dot”, “bubble”, “lollipop”, “geneheat”, “genechord”, “network”, “gomap”, “goheat”, “gotangram”, “wordcloud”, “upset”

pdf(paste("gotangram.pdf",sep=""))
plotEnrich(ego3, plot_type = "gotangram",main_text_size = 15,legend_text_size = 8, scale_ratio = 0.5, sim_method = "Rel")
dev.off()
```



# Network Plot

```{r}
library(patchwork)
library(igraph)
library(ggraph)
p1 <- plotEnrich(ego3, plot_type = "network", scale_ratio = 0.5)
p2 <- plotEnrich(ego3, plot_type = "network", 
                 layout = "circle", scale_ratio = 0.5)
p3 <- plotEnrich(ego3, plot_type = "network", 
                 layout = "grid", sim_method = "Wang",
                 up_color = "#a32a31", down_color = "#f7dcca",
                 scale_ratio = 0.5)
(p1 + p2) / p3 + plot_annotation(tag_levels = "A")



pdf(paste("Network.pdf",sep=""))
(p1 + p2) / p3 + plot_annotation(tag_levels = "A")
dev.off()
```



#  GO-specific: WEGO Plot

```{r}
# 1st step: prepare input IDs
id<- markers41$X

# 2nd step: prepare CC and MF gene sets
go_cc <- geneset::getGO(org = "human",ont = "cc")
go_mf <- geneset::getGO(org = "human",ont = "mf")


# 3rd step: analysis
ego_cc <- genORA(id, geneset = go_cc)
ego_mf <- genORA(id, geneset = go_mf)


# 4th step: merge two data frames
# Note: each data frame should add new column "Ontology"
ego_cc <- ego_cc %>% dplyr::mutate(Ontology = "cc") %>% dplyr::rename(ID = 1)
ego_mf <- ego_mf %>% dplyr::mutate(Ontology = "mf") %>% dplyr::rename(ID = 1)

all_ego <- rbind(ego_cc,ego_mf)
```


```{r }
plotEnrich(all_ego, plot_type = "wego", n_term = 5)

pdf(paste("WEGOPlot.pdf",sep=""))
plotEnrich(all_ego, plot_type = "wego", n_term = 5)
dev.off()
```

# GO-specific: Map Plot

```{r}
library(igraph)
library(ggraph)
plotEnrich(ego3, plot_type = "gomap", wrap_length = 25,
           up_color = '#a32a31',down_color = '#3665a6')

pdf(paste("MapPlot.pdf",sep=""))
plotEnrich(ego3, plot_type = "gomap", wrap_length = 25,
           up_color = '#a32a31',down_color = '#3665a6')
dev.off()
```

# GO-specific: Terms Heatmap Plot

```{r}
plotEnrich(ego3, plot_type = "goheat", sim_method = "Rel")

pdf(paste("TermsHeatmap.pdf",sep=""))
plotEnrich(ego3, plot_type = "goheat", sim_method = "Rel")
dev.off()
```


# Plot Theme

```{r}
library(patchwork)
p1 <- plotEnrich(ego3, plot_type = "dot")
p2 <- plotEnrich(ego3,
  plot_type = "dot",
  main_text_size = 10,
  legend_text_size = 10
)

p3 <- plotEnrich(ego3,
  plot_type = "dot",
  border_thick = 3,
  remove_grid = F
)

p4 <- plotEnrich(ego3,
  plot_type = "dot",
  remove_main_text = T,
  remove_legend_text = T,
  remove_legend = T
)
p1 + p2 + p3 + p4 + plot_annotation(tag_levels = "A")


pdf(paste("PlotTheme.pdf",sep=""))
p1 + p2 + p3 + p4 + plot_annotation(tag_levels = "A")
dev.off()
```

#  Advanced Plot

```{r}
# 1st step: prepare input IDs
# Since the geneList is logFC decreasing ordered, we could take first 100 as up-regulated genes and vice versa.

markers41 <- markers41[order(markers41$avg_diff, decreasing = TRUE), ]
up_genes <- rownames(markers41[markers41$avg_diff > 0.65, ])
down_genes <- rownames(markers41[markers41$avg_diff < -0.5, ])
 
# 2nd step: prepare gene set
hg_gs <- geneset::getGO(org = "human",ont = "bp")

# 3rd step: ORA analysis separately
up_go <- genORA(up_genes, geneset = hg_gs)
down_go <- genORA(down_genes, geneset = hg_gs)
```


```{r fig.height=10}
plotEnrichAdv(up_go, down_go,
              plot_type = "one",
              term_metric = "FoldEnrich",
              stats_metric = "p.adjust",
              xlim_left = 25, xlim_right = 15) +
  theme(legend.position = c(0.2, 0.9))


pdf(paste("Advanced.pdf",sep=""))
plotEnrichAdv(up_go, down_go,
              plot_type = "one",
              term_metric = "FoldEnrich",
              stats_metric = "p.adjust",
              xlim_left = 25, xlim_right = 15) +
  theme(legend.position = c(0.2, 0.9))
dev.off()
```

```{r fig.height=10}
plotEnrichAdv(up_go, down_go,
              plot_type = "two",
              term_metric = "FoldEnrich",
              stats_metric = "pvalue",
              legend_text_size = 5
) +
  theme(legend.position = "none")


pdf(paste("Advanced2.pdf",sep=""))
plotEnrichAdv(up_go, down_go,
              plot_type = "two",
              term_metric = "FoldEnrich",
              stats_metric = "pvalue",
              legend_text_size = 5
) +
  theme(legend.position = "none")
dev.off()
```
